Remotely SST

### 2019-08-06 remote_SST.Rmd
SST.update

@@

```{r}
MUR_Lamberts_Bay <- read_csv("Data/MUR/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Sea_Point <- read_csv("Data/MUR/MUR_Sea Point_SST_timeseries_5nearest.csv")
MUR_Hout_Bay<- read_csv("Data/MUR/MUR_Hout Bay_SST_timeseries_5nearest.csv")

@@

@@

## Matching the Insitu data with the CMC SST data
insitu_CMC <- match_func(df = CMC) 
CMC_plot <- match_plot(df = insitu_CMC )
CMC_temp<- temp_plot(df = insitu_CMC)
```

>>>>

# Loading libraries

```{r}
library(tidyverse)
library(plyr)
library(lubridate)
library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(data.table)
library(heatwaveR)
library(viridis)
library(gridExtra)
library(fossil)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ggpubr)
library(ggpubr); theme_set(theme_pubr())# library(devtools)
```

@@

```{r}
load("~/Documents/Masters_2019/Upwelling_MCS/Data/SACTN_US.RData")

MUR_Lamberts_Bay <- read_csv("Data/MUR/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
MUR_Port_Nolloth <- read_csv("Data/MUR/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
MUR_Saldanha_Bay <- read_csv("Data/MUR/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
MUR_Sea_Point <- read_csv("Data/MUR/MUR_Sea Point_SST_timeseries_5nearest.csv")
MUR_Hout_Bay<- read_csv("Data/MUR/MUR_Hout Bay_SST_timeseries_5nearest.csv")

@@

# Upwelling and MCS

MUR_SST <- insitu_MUR %>% 
  select(date,temp_MUR, site) %>% 
  dplyr::rename(t = date) %>% 
  dplyr::rename(temp = temp_MUR)

filter_func <- function(df){
  filtered <- MUR_SST  %>%  
  filter(site == df) %>%
  select(-site) %>% 
  drop_na()
  return(filtered)
}

MUR_LB <- filter_func(df = "Lamberts Bay") 
MUR_SB <- filter_func(df = "Saldanha Bay") 
MUR_HB <- filter_func(df = "Hout Bay") 
MUR_PN <- filter_func(df = "Port Nolloth") 
MUR_SP <- filter_func(df = "Sea Point")

# MCS

MCS_func <- function(df){
  res_clim <- ts2clm(df, climatologyPeriod = c("2002-06-01", "2015-12-30"),
                   pctile = 10)
  return(res_clim)
}

PN_MCS <- MCS_func(df = MUR_PN)
LB_MCS <- MCS_func(df = MUR_LB)
SB_MCS <- MCS_func(df = MUR_SB)
SP_MCS <- MCS_func(df = MUR_SP)

HB_MCS <- ts2clm(MUR_HB, climatologyPeriod = c("2002-06-01", "2005-10-19"), # Climatological period differs to the rest
                   pctile = 10)

## Events
MCS_event <- function(df){
  detect <- detect_event(df, coldSpells = TRUE)
  return(detect)
}

PN_MCS_events <- MCS_func(df = PN_MCS)
LB_MCS_events <- MCS_func(df = LB_MCS)
SB_MCS_events <- MCS_func(df = SB_MCS)
SP_MCS_events <- MCS_func(df = SP_MCS)

HB_MCS_events <- detect_event(HB_MCS, coldSpells = TRUE) 
```

## Upwelling events - 30th percentile used as a threshold to detect upwellling events.

```{r}
upwell_func <- function(df){
  res_clim <- ts2clm(df, climatologyPeriod = c("2002-06-01", "2015-12-30"),
                   pctile = 30)
  return(res_clim)
}

PN_upwell <- upwell_func(df = MUR_PN)
LB_upwell <- upwell_func(df = MUR_LB)
SB_upwell <- upwell_func(df = MUR_SB)
SP_upwell <- upwell_func(df = MUR_SP)

HB_upwell <- ts2clm(MUR_HB, climatologyPeriod = c("2002-06-01", "2005-10-19"), # Climatological period differs to the rest
                   pctile = 10)

## Events
upwell_event <- function(df){
  detect <- detect_event(df, minDuration = 2, coldSpells = TRUE)
  return(detect)
}

PN_upwell_events <- MCS_func(df = PN_upwell)
LB_upwell_events <- MCS_func(df = LB_upwell)
SB_upwell_events <- MCS_func(df = SB_upwell)
SP_upwell_events <- MCS_func(df = SP_upwell)

HB_upwell_events <- detect_event(HB_upwell, minDuration = 2, coldSpells = TRUE)
```

@@

## Matching the Insitu data with the CMC SST data
insitu_CMC <- match_func(df = CMC)

CMC_SST <- insitu_CMC %>% 
  select(date,temp_CMC, site) %>% 
  dplyr::rename(t = date) %>% 
  dplyr::rename(temp = temp_CMC)

filter_func <- function(df){
  filtered <- CMC_SST  %>%  
  filter(site == df) %>%
  select(-site) %>% 
  drop_na()
  return(filtered)
}

CMC_LB <- filter_func(df = "Lamberts Bay") 
CMC_SB <- filter_func(df = "Saldanha Bay") 
CMC_HB <- filter_func(df = "Hout Bay") 
CMC_PN <- filter_func(df = "Port Nolloth") 
CMC_SP <- filter_func(df = "Sea Point")

# MCS

MCS_func <- function(df){
  res_clim <- ts2clm(df, climatologyPeriod = c("1991-09-01", "2015-12-30"),
                   pctile = 10)
  return(res_clim)
}

PN_MCS <- MCS_func(df = CMC_PN)
LB_MCS <- MCS_func(df = CMC_LB)
SB_MCS <- MCS_func(df = CMC_SB)
SP_MCS <- MCS_func(df = CMC_SP)

HB_MCS <- ts2clm(CMC_HB, climatologyPeriod = c("2002-06-01", "2005-10-19"), # Climatological period differs to the rest
                   pctile = 10)

## Events
MCS_event <- function(df){
  detect <- detect_event(df, coldSpells = TRUE)
  return(detect)
}

PN_MCS_events <- MCS_func(df = PN_MCS)
LB_MCS_events <- MCS_func(df = LB_MCS)
SB_MCS_events <- MCS_func(df = SB_MCS)
SP_MCS_events <- MCS_func(df = SP_MCS)

HB_MCS_events <- detect_event(HB_MCS, coldSpells = TRUE) 
```
